### 2022-05-11 supplement.Rmd
Prettify main (within) selection models

@@

```{r, tabs2, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Meta-analysis of mental rotation",
    "Meta-regression of mental rotation",
    "Meta-analysis of gender differences"
  ),
  list(res_freq, res_reg_freq, res_gender_freq),
  function(name, res) {
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      # Add variances
      bind_rows(tibble(
        Parameter = res$s.name,
        Estimate = print_num(res$sigma2)
      ))
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$",
      "$\\sigma_{\\text{Article}}^2$",
      "$\\sigma_{\\text{Experiment}}^2$",
      "Intercept (Hedges' $g$)",
      "Female - mixed",
      "Male - female",
      "Age (per year)",
      "Habituation - VoE",
      "(Female - mixed) $\\times$ age",
      "(Male - female) $\\times$ age",
      "$\\sigma_{\\text{Article}}^2$",
      "$\\sigma_{\\text{Experiment}}^2$",
      "Hedges' $g$",
      "$\\sigma_{\\text{Article}}^2$",
      "$\\sigma_{\\text{Experiment}}^2$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

@@

```{r, trim_and_fill_within}

# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# run trim and fill
res_tf <- trimfill(r_mod)
print(res_tf)
res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

summ_brm <- list(intercept = res_tf$beta)
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# # Create funnel plot
plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

@@

```{r,selection_models_within}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
print(sel_mod)
print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# 4 DIFFERENT STEP FUNCTION MODELS
# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
tab <- data.frame(
  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))

sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)

print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')

interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"

```

```{r, tabs_trimfill_selectionmodels_within, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model: severe two-tailed"
  ),
    list(
      r_mod,
      res_tf,
      sel_mod,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed
      ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

# Save the table
write_csv(tab_freq, file = here(tables_dir, "robustness_freq.csv"))
```

```{r, trim_and_fill_gender}
dat=dat_gender

# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# run trim and fill
res_tf <- trimfill(r_mod)
print(res_tf)
# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

summ_brm <- list(intercept = res_tf$beta)
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# # Create funnel plot
plotdata <- as.data.frame(list(yi = res_tf$yi, vi = sqrt(res_tf$vi)))
ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

```{r,selection_models_gender}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
print(sel_mod)
# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# 4 DIFFERENT STEP FUNCTION MODELS
# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
tab <- data.frame(
  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))

sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)

@@

# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"

```

```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model: severe two-tailed"
  ),
    list(
      r_mod,
      res_tf,
      sel_mod,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed
      ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

>>>>

## Supplementary Methods 2 | Bias correction and sensitivity analysis for frequentist results

We used a simplified two-level version (i.e., dropping the article level) of our frequentist three-level model to further correct our results for publication bias. We conducted a trim-and-fill analysis [@duval2000] to impute possible effect sizes of non-published experiments and then observed their influence on the meta-analytic effect size (Supplementary Tables 8 and 9).

Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published. We ran one selection model assuming a weight function with fixed p-value cutoffs at p = .01, p = .05, and p = 0.3[@vevea1995], as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005]. These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).

@@

```{r, tabs2, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  list(res_freq, res_reg_freq, res_gender_freq),
  c(
    "Meta-analysis of mental rotation",
    "Meta-regression of mental rotation",
    "Meta-analysis of gender differences"
  ),
  ~ print_res_freq_table(
    res_freq = .x, label_1 = .y, label_col_1 = "Model", print_sigma2s = TRUE
  )
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$",
      "$\\sigma_{\\text{Article}}^2$",
      "$\\sigma_{\\text{Experiment}}^2$",
      "Intercept (Hedges' $g$)",
      "Female - mixed",
      "Male - female",
      "Age (per year)",
      "Habituation - VoE",
      "(Female - mixed) $\\times$ age",
      "(Male - female) $\\times$ age",
      "$\\sigma_{\\text{Article}}^2$",
      "$\\sigma_{\\text{Experiment}}^2$",
      "Hedges' $g$",
      "$\\sigma_{\\text{Article}}^2$",
      "$\\sigma_{\\text{Experiment}}^2$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

@@

```{r, trim_fill_selection}
# Re-fit frequentist meta-analysis using a two-level model
res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)

# Run trim-and-fill analysis
res_trim_fill <- trimfill(res_freq_2)
print(res_trim_fill)

# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
res_selection_weights <- selmodel(
  res_freq_2,
  type = "stepfun", steps = c(0.01, .05, .3, 1)
)
print(res_selection_weights)

# More selection models based on four different step functions
tibble(
  delta_one_tailed_moderate = c(
    1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55,
    0.50, 0.50, 0.50, 0.50, 0.50, 0.50
  ),
  delta_one_tailed_severe = c(
    1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35,
    0.30, 0.25, 0.10, 0.10, 0.10, 0.10
  ),
  delta_two_tailed_moderate = c(
    1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60,
    0.75, 0.80, 0.90, 0.95, 0.99, 1.00
  ),
  delta_two_tailed_severe = c(
    1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25,
    0.50, 0.60, 0.75, 0.90, 0.99, 1.00
  )
) %>%
  print() %>%
  map(function(delta) {
    selmodel(
      res_freq_2,
      type = "stepfun",
      steps = c(
        0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50,
        0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1
      ),
      delta = delta
    )
  }) -> res_selection_steps
print(res_selection_steps)
```

```{r, tabs8, include=TRUE}
# Combine all trim-and-fill and selection models into one table
tibble(
  res = c(
    list(res_freq_2, res_trim_fill, res_selection_weights), res_selection_steps
  ),
  label_1 = c(
    "Two-level model", "Trim-and-fill model",
    "Selection models:", "", "", "", ""
  ),
  label_2 = c(
    "", "", "Weight function [.01, .05, .30]",
    "One-tailed, moderate bias", "One-tailed, severe bias",
    "Two-tailed, moderate bias", "Two-tailed, severe bias"
  )
) %>%
  pmap_dfr(
    ~ print_res_freq_table(
      res_freq = ..1, label_1 = ..2, label_2 = ..3,
      label_col_1 = "Model", label_col_2 = " ", print_sigma2s = FALSE
    )
  ) %>%
  select(-Parameter) %>%
  rename(`Hedges' $g$` = Estimate) -> tab_trim_fill_selection

# Save the table
write_csv(
  tab_trim_fill_selection,
  file = here(tables_dir, "trim_fill_selection.csv")
)

# Display the table
apa_table(
  tab_trim_fill_selection,
  align = "llccccc",
  caption = "Trim-and-fill and selection model analyses",
  font_size = "scriptsize",
  escape = FALSE
)
```

```{r, figs4, include=TRUE, fig.width=6, fig.height=3.5, out.width="50%"}
# Compute new funnel, taking into account the trim-and-fill results
funnel_trim_fill <- with(
  list(
    z_crit_05 = stats::qnorm(0.975),
    max_se = max(sqrt(res_trim_fill$vi)) + 0.05
  ),
  {
    data.frame(
      x = c(
        res_trim_fill$b - z_crit_05 * sqrt(max_se^2),
        res_trim_fill$b,
        res_trim_fill$b + z_crit_05 * sqrt(max_se^2)
      ),
      y = c(max_se, 0, max_se)
    )
  }
)

# Create new funnel plot, enhanced by the filled in studies
trim_fill_color <- "#e42536"
plots_funnel[[1]] +
  # Add trim and fill funnel
  geom_path(
    data = funnel_trim_fill,
    aes(x = x, y = y),
    color = trim_fill_color
  ) +
  geom_vline(xintercept = res_trim_fill$b, color = trim_fill_color) +
  # Add filled in studies
  geom_point(
    data = with(res_trim_fill, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
    color = trim_fill_color, shape = 0
  )

# Save the plot
ggsave(here(figures_dir, "funnel_trim_fill.pdf"), width = 6, height = 3.5)
```

```{r, trim_and_fill_gender}
dat <- dat_gender

# random-effects 2 level model
res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)

# run trim and fill
res_trim_fill <- trimfill(res_freq_2)
print(res_trim_fill)
# res_string <- "The publication-bias-corrected effect size of mental rotation was 0.16"

summ_brm <- list(intercept = res_trim_fill$beta)
# Compute funnel
funnel_z_crit <- stats::qnorm(0.975)
funnel_max_se <- 0.5 # A bit larger than the largest observed `sei` in `dat`
funnel_tau2 <- 0 # We don't take heterogeneity into account, only the SE
funnel <- data.frame(
  x = c(
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2),
    summ_brm$intercept - funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_tau2),
    summ_brm$intercept + funnel_z_crit * sqrt(funnel_max_se^2 + funnel_tau2)
  ),
  y = c(funnel_max_se, 0, 0, funnel_max_se)
)

# # Create funnel plot
plotdata <- as.data.frame(list(yi = res_trim_fill$yi, vi = sqrt(res_trim_fill$vi)))
ggplot(plotdata, aes(x = yi, y = sqrt(vi))) +
  geom_vline(xintercept = seq(-2, 2, 0.5), color = "grey90") +
  # Meta-analytic effect size
  geom_vline(xintercept = summ_brm$intercept, color = "black") +
  # Experiment-specific effect sizes
  geom_point(shape = 0) +
  # Funnel
  geom_path(data = funnel, aes(x = x, y = y), linetype = "dashed") +
  # Styling
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  scale_y_reverse() +
  coord_cartesian(
    xlim = c(-2.5, 2.5),
    ylim = c(funnel_max_se, 0),
    expand = FALSE
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    y = "Standard error",
  ) +
  theme_classic() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(family = "Helvetica", color = "black")
  )

@@

```{r,selection_models_gender}
# random-effects 2 level model
res_freq_2 <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod <- selmodel(res_freq_2, type = "stepfun", steps = c(0.01, .05, .3, 1), verbose = TRUE)
print(sel_mod)
# print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# 4 DIFFERENT STEP FUNCTION MODELS
# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that
# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
tab <- data.frame(
  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00)
)

sel_moderateonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.1, verbose = TRUE)
sel_severeonetailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.1, verbose = TRUE)
sel_moderatetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.mod.2, verbose = TRUE)
sel_severetwotailed <- selmodel(res_freq_2, type = "stepfun", steps = tab$steps, delta = tab$delta.sev.2, verbose = TRUE)

@@

# interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"
```

```{r, tabs_trimfill_selectionmodels_gender, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: weight-function [0.01, 0.05, 0.3]",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
    "Selection model: severe two-tailed"
  ),
  list(
    res_freq_2,
    res_trim_fill,
    sel_mod,
    sel_moderateonetailed,
    sel_severeonetailed,
    sel_moderatetwotailed,
    sel_severetwotailed
  ),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq
